### 2022-11-03 files/Chapter3/dynamicconvergence.tex
Fixing missing work in Chapter 3.

To start, the authors of \cite{BV13} formulate the Galerkin Approximation of Problem GVar.

@@

For any function $w_h$ in $S^h$, $w_h$ can be expressed as a linear combination
\begin{eqnarray*}
	w_h = \sum_{j=1}^n w_j \phi_j.
\end{eqnarray*} Define a vector valued function $\bar{w} = \langle w_1 \ w_2 \ ... \ w_n \rangle$ for each $w_h \in S^h$. The problem of solving the Galerkin Approximation is denoted by Problem GVar$^h$.

@@

\subsection{Error estimates}
Given that the assumptions \textbf{A1}-\textbf{A4} of Section 2 is satisfied, and $f$ is continuous, there exists unique solutions for  Problem GVar and Problem GVar$^h$. It remains only to show that the solution of Problem GVar$^h$ denoted by $u^h$ converges to the solution of Problem GVar denoted by $u$ as $h$ is decreased.\\

@@

@@

The following two assumptions are made in \cite{BV13}.
\subsubsection*{Assumptions}
\begin{itemize}
	\item[] \textbf{B1} - The solution $u \in C(J,V)$ of Problem GVar$^h$ has the property that $(Pu) \in C^2(J)$.

@@

To solve the error estimate $e$, the following theorem is proved in \cite{BV13}.

As mentioned before, the authors use Finite Element Analysis to obtain an error estimate for $e$. What follows is a discussion of the approach used in \cite{BV13}.

\subsection{System of ordinary differential equations}
Consider the standard FEM matrices defined by
\begin{eqnarray*}
	K_{ij} & = & b(\phi_j, \phi_i)\\
	C_{ij} & = & a(\phi_j, \phi_i)\\
	M_{ij} & = & c(\phi_j, \phi_i)\\
	F_{i}(t) & = & b(f(t), \phi_i)_X
\end{eqnarray*}

\newtheorem{DC_Prop2}{Proposition}
\begin{DC_Prop2}
	If $F\in C(J)$, then Problem ODE has a unique solution for each pair of vectors $\bar{d}$ and $\bar{v}.$
\end{DC_Prop2}

\newtheorem{DC_Prop3}[DC_Prop2]{Proposition}
\begin{DC_Prop3}
	Suppose $M, K, C, F,\bar{d}$ and $\bar{v}$ are defined as above. Then, the function $u_{h}$ is a solution of Problem GVar$^{h}$ if and only if the function $\bar{u}$ is a solution of Problem ODE.
\end{DC_Prop3}

In \eqref{error_e}, the authors divide the error $e$ into a semi-discrete term and a fully discrete term. The two terms are investigated separately in \cite{BV13}.

\subsection{Semi-discrete error estimate}

@@

The authors of \cite{BV13} introduce two assumptions.
\subsubsection*{Assumptions} 
\begin{itemize}
	\item[] \textbf{E1} - The solution $u$ of Problem GVar has the property that $(Pu) \in C^2(0,T)$.

	\item[] \textbf{E2} -There exists a subspace $H$ of $V$ and a positive integer $\alpha$ such that if $w\in H,$ then
	\begin{eqnarray*}
		\inf_{v\in S^{h}}\Vert w-v\Vert_{V}\leq\hat{C}h^{\alpha}|||w|||_{H},
	\end{eqnarray*}
	where $|||w|||_{H}$ is a norm or semi-norm for $H.$
\end{itemize}

>>>>

Before we can look at the results of \cite{BV13}, some preparation is required. To start, the authors of \cite{BV13} formulate the Galerkin Approximation of Problem GVar.

@@

For any function $w_h$ in $S^h$, $w_h$ can be expressed as a linear combination
\begin{eqnarray*}
	w_h = \sum_{j=1}^n w_j \phi_j.
\end{eqnarray*} Define a vector valued function $\bar{w} = \langle w_1,w_2,...,w_n \rangle$ for each $w_h \in S^h$. The problem of solving the Galerkin Approximation is denoted by Problem GVar$^h$.

@@

\subsection{System of ordinary differential equations}
Consider the standard FEM matrices defined by
\begin{eqnarray*}
	K_{ij} & = & b(\phi_j, \phi_i)\\
	C_{ij} & = & a(\phi_j, \phi_i)\\
	M_{ij} & = & c(\phi_j, \phi_i)\\
	F_{i}(t) & = & b(f(t), \phi_i)
\end{eqnarray*}

\newtheorem{DC_Prop2}{Proposition}
\begin{DC_Prop2}
	If $F\in C(J)$, then Problem ODE has a unique solution for each pair of vectors $\bar{u}^h_0$ and $\bar{u}^h_1$
\end{DC_Prop2}

\newtheorem{DC_Prop3}[DC_Prop2]{Proposition}
\begin{DC_Prop3}
	Suppose $M, K, C, F,\bar{u}^h_0$ and $\bar{u}^h_1$ are defined as above. Then, the function $u_{h}$ is a solution of Problem GVar$^{h}$ if and only if the function $\bar{u}$ is a solution of Problem ODE.
\end{DC_Prop3}

\subsection{Error estimates}\label{e_est}
Given that the assumptions \textbf{A1}-\textbf{A4} of Section 2 is satisfied, and $f$ is continuous, there exists unique solutions for  Problem GVar and Problem GVar$^h$. It remains only to show that the solution of Problem GVar$^h$ denoted by $u^h$ converges to the solution of Problem GVar denoted by $u$ as $h$ is decreased.\\

@@

The error $e$, can now be expressed as
\begin{eqnarray}
	e(t_k) = u(t_k) - u^h_k & = & [u(t_k)-u_h(t_k)] + [u_h(t_k) - u^h_k]. \label{error_e}
\end{eqnarray}

In \eqref{error_e}, the authors divide the error $e$ into a semi-discrete term and a fully discrete term. The two terms are investigated as seperate problems in \cite{BV13}.\\

@@

\subsection{Obtaining the error estimate}
In this section we will show how the error estimate in Theorem 2 is obtained in \cite{BV13}.\\

The following two assumptions are made in \cite{BV13}.

\subsubsection*{Assumptions}
\begin{itemize}
	\item[] \textbf{B1} - The solution $u \in C(J,V)$ of Problem GVar$^h$ has the property that $(Pu) \in C^2(J)$.

@@

The projection $P$ in section \eqref{e_est} is defined in \cite{BV13} as
\begin{eqnarray*}
	b(u-P_hu,v) = 0 \ \ \ \textrm{ for all } v \in V.
\end{eqnarray*}

From assumption \textbf{B1}, $Pu \in C^2(J)$ and by the definition $P$, $P$ is a projection with respect to the inner product $b$.\\

Subtracting \eqref{GV_PB1} from \eqref{DC_E2} gives
\begin{eqnarray*}
	c(u''(t)-u''_h(t),v) + a(u'(t)-u'_h(t),v) + b(u(t)-u_h(t),v) = 0
\end{eqnarray*}

Using the definition of the error $e^h$ while also adding and subtracting $Pu(t)$ in the bilinear form $b$, we can write
\begin{eqnarray*}
	c(e''(t),v) + a(e'(t),v) + b(u(t) - Pu(t),v) + b(Pu(t) +u_h(t),v)- = 0
\end{eqnarray*}

It then follows from the definitions of the error $e$ and the projection $P$ that 
\begin{eqnarray*}
	c(e''(t),v) + a(e'(t),v) + b(e(t),v) = 0
\end{eqnarray*}

In \cite{BV13}, this is presented as a proposition.
\newtheorem{DC_Prop1}{Proposition}
\begin{DC_Prop1}
	If $u$ is the solution of Problem GVar and $u$ satisfies assumption \textbf{B1}, then

	\begin{eqnarray}
		c(e''(t),v) + a(e'(t),v) + b(e(t),v) = 0 \ \ \ \textrm{ for all } v \in V.
	\end{eqnarray}
\end{DC_Prop1}

Using this proposition, the authors of \cite{BV13} derive a generalized error estimate for the error $e = Pu - u_h$.

\newtheorem{lem_1}{Lemma}
\begin{lem_1}
	If $u$ is the solution of Problem GVar and $u$ satisfies assumption \textbf{B1}, then
	\begin{eqnarray}
		\Vert e(t)\Vert_{W} \leq \sqrt{2} \left( \Vert e(0) \Vert_W + 3T\Vert e'_h(0) \Vert_W + 3 \int_o^T \Vert e'_p(t)\Vert_W + 3K_\alpha T \Vert e_h(0) \Vert_W + 3K_\alpha \int_0^T \Vert e_p(t) \Vert_W \right).
	\end{eqnarray}
\end{lem_1}

In chapter 2, it was explained that the models of this dissertation have weak damping, i.e. $a = 0$. Therefore, the error estimate in Lemma 1 can be simplified. This is given in \cite{BV13} as a corollary.

\newtheorem{col_1}{Corollary}
\begin{col_1}
	If $u$ is the solution of Problem GVar with $a = 0$ and $u$ satisfies assumption \textbf{B1}, then
	\begin{eqnarray}
		\Vert e(t)\Vert_{W} \leq \sqrt{2} \Vert e(0) \Vert_W + 4\sqrt{T}\max_{t \in [0,T]} \Vert e'_p(t) \Vert_W.
	\end{eqnarray}
\end{col_1}

\subsection{Semi-discrete problem}

@@
